Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
speling
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@75 43ef1190-90fd-4dd7-a769-d0121f02b80e

However, I have found the current state of the art in benchmarking
lacking in its use of statistics, which motivates two distincts
directions of work: \emph{Statistical experimental planning and execution in
benchmarking} and \emph{statistical methods to optimize SPARQL queries
in a federated regime}.

@@

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms
and other data. However, histogram approaches generally suffers from
the problem that they grow too large or become a insufficiently
accurate digest, especially in face of very heterogenous data.

@@

Another approach that I have not seen used in the literature is to use
parameterized statistics. This would amount to attempt fitting data to
a known distribution function and expose which distribution and its
parameters in the service description.

>>>>

However, I have found the current state of the art in benchmarking
lacking in its use of statistics, which motivates two distinct
directions of work: \emph{Statistical experimental planning and execution in
benchmarking} and \emph{statistical methods to optimize SPARQL queries
in a federated regime}.

@@

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms
and other data. However, histogram approaches generally suffers from
the problem that they grow too large or become a insufficiently
accurate digest, especially in face of very heterogeneous data.

@@

Another approach that I have not seen used in the literature is to use
parametrized statistics. This would amount to attempt fitting data to
a known distribution function and expose which distribution and its
parameters in the service description.
